Multi-target detection with application to cryo-electron microscopy

### 2019-03-04 inverse_problems/inverse_problems.tex
abstract

We consider the multi-target detection problem of recovering a set of signals that appear 
multiple times at unknown locations in a noisy measurement.
In the low noise regime, one can estimate the signals by first detect their occurrences and then cluster them.
In the high noise regime neither detection nor  clustering can be performed reliably and thus such a strategy is destined to fail.  
By employing autocorrelation analysis, we show that in some cases the signals themselves can be estimated  without detecting their occurrences. 
To estimate the signals, we derive simple relations between the autocorrelations of the observations and those of the signals. These autocorrelations can be estimate accurately in any noise level given sufficiently long measurement. 
To recover the signals from their autocorrelations, we suggest to solve a nonlinear least-squares. 
We provide rigorous analysis for the special case in which the same signal appears multiple times in the data, and demonstrate numerically the effectiveness of the method in a variety of settings.

The main goal of this work is to supply theoretical and numerical support for a recent suggestion to  estimate the 3-D structure of single particles using cryo-electron microscopy in extreme noise levels~\cite{bendory2018toward}.

>>>>

We consider the multi-target detection problem of recovering a set of signals that appear 
multiple times at unknown locations in a noisy measurement.
In the low noise regime, one can estimate the signals by first detect their occurrences and then cluster them.
However, in the high noise regime neither detection nor  clustering can be performed reliably and thus such a strategy is destined to fail.  
By employing autocorrelation analysis, we show that the impossibility to detect and cluster signals' occurrences in high noise levels does not necessarily impose limitations on signal estimation.
Specifically, to estimate the signals, we derive simple relations between the autocorrelations of the observation and those of the signals. These autocorrelations can be estimated accurately in any noise level given sufficiently long measurement. 
To recover the signals from their autocorrelations, we suggest to solve a nonlinear least-squares. 
We provide rigorous analysis for the special case in which a single signal appears multiple times in the data, and demonstrate numerically the effectiveness of the method in a variety of settings.

The main goal of this work is to provide theoretical and numerical support for a recently proposed framework to elucidate 3-D structures of biological macromolecules using cryo-electron microscopy in extreme noise levels~\cite{bendory2018toward}.
